Price of Anarchy for Mean Field Games

### 2018-07-27 PoA.tex
Prop 7 Case 4 finished

% proposition b1 bar
\begin{proposition}\label{prop:b1_b1bar}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and $Var(\xi)>0$, and:
	\begin{equation*}
	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2
	\end{equation*}
	then:
	\begin{equation*}
	\begin{split}
	    \lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1,\\
	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{split}
	\end{equation*}
\end{proposition}
\begin{proof}
	First, we consider $b_1 \to 0$. We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$. Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$. Next, we show that the three sequences are uniformly bounded. Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$. There exists a $b_1^*$ such that $\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|<\epsilon$ and $\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right|<\epsilon$ for each $b_1<b_1^*$. Then for each $b_1<b_1^*$ and $t\in[0,T]$, we have:
	\begin{equation*}
		\left|u^{b_1}_t\right| \leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
		\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon} := c
	\end{equation*}
	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2$, we have $D^{u} \neq D^{w,b_1}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.

@@

	Todo: case $b_1 \to \infty$ and $\bar{b}_1 \to \infty$.

	Now, consider $\bar{b}_1 \to \infty$.
	Since $\lim_{\bar{b}_1 \to \infty} |A^{u,\bar{b}_1}|=\infty$, we have:
	\begin{equation*}
	\begin{split}
	\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u&=2 \sqrt{(A^{u,\bar{b}_1})^2+BC^u} \\
	&\xrightarrow[\bar{b}_1 \to \infty]{}\infty,
	\end{split}
	\end{equation*}
	and
	\begin{equation*}
	\begin{split}
	-\delta^{-,\bar{b}_1}_u&=A^{u,\bar{b}_1}+\sqrt{(A^{u,\bar{b}_1})^2+BC^u} \\
	&\xrightarrow[\bar{b}_1 \to \infty]{}0.
	\end{split}
	\end{equation*}
	Therefore, it can be shown that for $t \in [0,T)$:
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty}\frac{u^{\bar{b}_1}_t}{\bar{b}_1}=\frac{1}{B}.
	\end{equation*}
	Similarly, for $t \in [0,T)$:
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty}\frac{w^{\bar{b}_1}_t}{\bar{b}_1}=\frac{2}{B}.
	\end{equation*}
	Thus,
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty} \left(\frac{u^{\bar{b}_1}_t}{\bar{b}_1}-\frac{w^{\bar{b}_1}_t}{\bar{b}_1}\right)^2=\frac{1}{B^2}.
	\end{equation*}

@@

	Now, consider:
	\begin{equation*}
	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{B}{2}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}} \left(\frac{u_t^{\bar{b}_1}}{\bar{b}_1} - \frac{w_t^{\bar{b}_1}}{\bar{b}_1}\right)^2 e^{2\int_0^t (b_1+\bar{b}_1-B u_s^{\bar{b}_1})ds} dt.
	\end{equation*}
	(ToDo: Show $\frac{u^{\bar{b}_1}_t}{\bar{b}_1} \to \frac{1}{B}$ and $\frac{w^{\bar{b}_1}_t}{\bar{b}_1} \to \frac{2}{B}$ UNIFORMLY for $t \in [0,T/2]$. OR show both are uniformly bounded and use the bounded convergence theorem.)

	Then for $\zeta:=\frac{1}{B^2}$, there exists $\bar{b}_1^{*,u,w}$ such that for $t\in[0,T/2]$ and $\bar{b}_1 \geq \bar{b}_1^{*,u,w}$,
	\begin{equation*}
	\left(\frac{u_t^{\bar{b}_1}}{\bar{b}_1} - \frac{w_t^{\bar{b}_1}}{\bar{b}_1}\right)^2 \geq \frac{1}{B^2}-\zeta=\frac{1}{2B^2}.
	\end{equation*}
	Then,
	\begin{equation*}
	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{1}{4B}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}}e^{2\int_0^t (b_1+\bar{b}_1-B u_s^{\bar{b}_1})ds} dt.
	\end{equation*}

	Since $\lim_{\bar{b}_1 \to \infty}B (D^{u})^2 + 2 A^{u,\bar{b}_1} D^{u} - C^{u}=-\infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) there exists a $\bar{b}_1^{*,dec}$ such that for $\bar{b}_1 \geq \bar{b}_1^{*,dec}$, $t \mapsto u_t^{\bar{b}_1}$ is decreasing, and thus, $(\bar{b}_1-B u_t^{\bar{b}_1})\geq (\bar{b}_1-B u_{0}^{\bar{b}_1})$.

	(ToDo: Show $(\bar{b}_1-B u_0^{\bar{b}_1}) \to 0$.)

	Let $\zeta_2>0$. Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) = 0$, there exists $\bar{b}_1^{*} \geq \max \{\bar{b}_1^{*,u,w},\bar{b}_1^{*,dec} \}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$,
	\begin{equation*}
	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{1}{4B}(\mathbb{E}(\xi))^2 \int_0^{\frac{T}{2}}e^{2tb_1}e^{-2t\zeta_2}dt=:c_{\Delta SC}>0,
	\end{equation*}
	and therefore:
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty}\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}>0.
	\end{equation*}
	Thus, we conclude:
	\begin{equation*}
	\begin{split}
	\lim_{\bar{b}_1 \to \infty}\frac{\Delta SC^{\bar{b}_1}}{SC^{MKV,\bar{b}_1}}=\lim_{\bar{b}_1 \to \infty}\frac{\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}}{\frac{1}{\bar{b}_1^2}SC^{MKV,\bar{b}_1}}=\infty,
	\end{split}
	\end{equation*}
	and therefore,
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty} PoA^{\bar{b}_1}=\infty.
	\end{equation*}

>>>>

% proposition b1 bar
\begin{proposition}\label{prop:b1_b1bar}
	Assuming (\ref{eq:assumptions}), the initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and $Var(\xi)>0$, and:
	\begin{equation*}
	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2,
	\end{equation*}
	\begin{equation*}
	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) >0,
	\end{equation*}
	then:
	\begin{equation*}
	\begin{split}
	    \lim_{b_1 \to 0} PoA =: PoA^{0,b_1} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{0,\bar{b}_1} > 1,\\
	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{split}
	\end{equation*}
\end{proposition}
\begin{proof}
	First, we consider $b_1 \to 0$. We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$. Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$. Next, we show that the three sequences are uniformly bounded. Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$. There exists a $b_1^*$ such that $\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|<\epsilon$ and $\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right|<\epsilon$ for each $b_1<b_1^*$. Then for each $b_1<b_1^*$ and $t\in[0,T]$, we have:
	\begin{equation*}
		\left|u^{b_1}_t\right| \leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
		\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon} := c
	\end{equation*}
	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2$, we have $D^{u} \neq D^{w,b_1}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.

@@

	Todo: case $b_1 \to \infty$.

	Now, consider $\bar{b}_1 \to \infty$.
	Since $A^{u,\bar{b}_1}<0$ and $\lim_{\bar{b}_1 \to \infty} |A^{u,\bar{b}_1}|=\infty$, we have the following limits:
	\begin{equation*}
	\begin{split}
	\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u&=2 \sqrt{(A^{u,\bar{b}_1})^2+BC^u} \xrightarrow[\bar{b}_1 \to \infty]{}\infty,\\
	-\delta^{-,\bar{b}_1}_u&=A^{u,\bar{b}_1}+\sqrt{(A^{u,\bar{b}_1})^2+BC^u}\xrightarrow[\bar{b}_1 \to \infty]{}0,\\
	\frac{\delta^{+,\bar{b}_1}_u}{\bar{b}_1}&=\frac{b_1+\frac{\bar{b}_1}{2}}{\bar{b}_1} \frac{\sqrt{\left(\frac{\bar{b}_1}{2}\right)^2+BC^u}}{\bar{b}_1}\xrightarrow[\bar{b}_1 \to \infty]{} \frac{1}{2}+\frac{1}{2}=1
	\end{split}
	\end{equation*}
	We also have for $t\in [0,T)$:
	\begin{equation*}
	\begin{split}
	\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}\leq(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}
	\xrightarrow[\bar{b}_1 \to \infty]{}0,
	\end{split}
	\end{equation*}
	which implies:
	\begin{equation*}
	\lim_{\bar{b}_1\to \infty}\delta^{+,\bar{b}_1}_ue^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}=0.
	\end{equation*}
	Therefore, for $t \in [0,T)$:
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty}\frac{u^{\bar{b}_1}_t}{\bar{b}_1}=\frac{1}{B}.
	\end{equation*}
	By the same arguments, we have for $t \in [0,T)$:
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty}\frac{w^{\bar{b}_1}_t}{\bar{b}_1}=\frac{2}{B}.
	\end{equation*}
	Thus,
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty} \left(\frac{u^{\bar{b}_1}_t}{\bar{b}_1}-\frac{w^{\bar{b}_1}_t}{\bar{b}_1}\right)^2=\frac{1}{B^2}.
	\end{equation*}

@@

	Now, consider:
	\begin{equation}
	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{B}{2}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}} \left(\frac{u_t^{\bar{b}_1}}{\bar{b}_1} - \frac{w_t^{\bar{b}_1}}{\bar{b}_1}\right)^2 e^{2\int_0^t (b_1+\bar{b}_1-B u_s^{\bar{b}_1})ds} dt.
	\label{eq:prop_7_case_4_numerator}
	\end{equation}
	%(ToDo: Show $\frac{u^{\bar{b}_1}_t}{\bar{b}_1} \to \frac{1}{B}$ and $\frac{w^{\bar{b}_1}_t}{\bar{b}_1} \to \frac{2}{B}$ UNIFORMLY for $t \in [0,T/2]$. OR show both are uniformly bounded and use the bounded convergence theorem.)

	%Then for $\zeta:=\frac{1}{B^2}$, there exists $\bar{b}_1^{*,u,w}$ such that for $t\in[0,T/2]$ and $\bar{b}_1 \geq \bar{b}_1^{*,u,w}$,
	%\begin{equation*}
	%\left(\frac{u_t^{\bar{b}_1}}{\bar{b}_1} - \frac{w_t^{\bar{b}_1}}{\bar{b}_1}\right)^2 \geq \frac{1}{B^2}-\zeta=\frac{1}{2B^2}.
	%\end{equation*}
	%Then,
	%\begin{equation*}
	%\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq \frac{1}{4B}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}}e^{2\int_0^t (b_1+\bar{b}_1-B u_s^{\bar{b}_1})ds} dt.
	%\end{equation*}
	Since $\lim_{\bar{b}_1 \to \infty}B (D^{u})^2 + 2 A^{u,\bar{b}_1} D^{u} - C^{u}=-\infty$, from equation (\ref{eq:riccati_ut_sol_deriv}) there exists a $\bar{b}_1^{*,dec}$ such that for $\bar{b}_1 \geq \bar{b}_1^{*,dec}$, $t \mapsto u_t^{\bar{b}_1}$ is decreasing, and thus, $(\bar{b}_1-B u_t^{\bar{b}_1})\geq (\bar{b}_1-B u_{0}^{\bar{b}_1})$. Next, we will show $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1})=c$. We have the following limits for $t\in[0,T)$:
	\begin{equation*}
	\begin{split}
	\lim_{\bar{b}_1 \to \infty}\bar{b}_1-\delta^{+,\bar{b}_1}_u&=-2b_1\\
	\lim_{\bar{b}_1 \to \infty}-\delta^{-,\bar{b}_1}_u\bar{b}_1&=BC^u\\
	\lim_{\bar{b}_1 \to \infty}\delta^{+,\bar{b}_1}_u\bar{b}_1e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}&=0\\
	\lim_{\bar{b}_1 \to \infty}(\delta^{-,\bar{b}_1}_u-\bar{b}_1)e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)(T-t)}&=0,
	\end{split}
	\end{equation*}
	and thus, with the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) >0$ which implies $D^u>0$,
	\begin{equation*}
	\begin{split}
	\bar{b}_1-Bu^{\bar{b}_1}_0&=\frac{-BC^u+BD^u(\bar{b}_1-\delta^{+,\bar{b}_1}_u)-\delta^{-,\bar{b}_1}_u\bar{b}_1+(\delta^{+,\bar{b}_1}_u\bar{b}_1+BC^u+BD^u(\delta^{-,\bar{b}_1}_u-\bar{b}_1))e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)T}}{BD^u-\delta^{-,\bar{b}_1}_u+(\delta^{+,\bar{b}_1}_u-BD^u) e^{-(\delta^{+,\bar{b}_1}_u-\delta^{-,\bar{b}_1}_u)T}} \\
	&\xrightarrow[\bar{b}_1 \to \infty]{}-2b_1.
	\end{split}
	\end{equation*}

	Since $\lim_{\bar{b}_1 \to \infty}(\bar{b}_1-B u_0^{\bar{b}_1}) =-2b_1$, there exists $\bar{b}_1^{*}\geq\bar{b}_1^{*,dec}$, such that for $\bar{b}_1 \geq \bar{b}_1^{*}$, $(\bar{b}_1-B u_0^{\bar{b}_1}) \geq -3b_1$. Returning to equation (\ref{eq:prop_7_case_4_numerator}), we have for $\bar{b}_1 \geq \bar{b}^*_1$:
	\begin{equation*}
	\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}\geq\frac{B}{2}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}} \left(\frac{u_t^{\bar{b}_1}}{\bar{b}_1} - \frac{w_t^{\bar{b}_1}}{\bar{b}_1}\right)^2 e^{2(b_1-3b_1)t}dt.
	\end{equation*}
	By the bounded convergence theorem,
	\begin{equation*}
	=\frac{B}{2}(\mathbb{E}(\xi))^2\int_{0}^{\frac{T}{2}} \frac{1}{B^2} e^{-4b_1t}dt=:c>0.
	\end{equation*}	
	Therefore,
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty}\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}>0,
	\end{equation*}
	and thus,
	\begin{equation*}
	\begin{split}
	\lim_{\bar{b}_1 \to \infty}\frac{\Delta SC^{\bar{b}_1}}{SC^{MKV,\bar{b}_1}}=\lim_{\bar{b}_1 \to \infty}\frac{\frac{1}{\bar{b}_1^2}\Delta SC^{\bar{b}_1}}{\frac{1}{\bar{b}_1^2}SC^{MKV,\bar{b}_1}}=\infty.
	\end{split}
	\end{equation*}
	We conclude:
	\begin{equation*}
	\lim_{\bar{b}_1 \to \infty} PoA^{\bar{b}_1}=\infty.
	\end{equation*}
